Sharing statistics for SPARQL Federation optimization, with emphasis on benchmark quality

### 2012-03-06 eswc-2012/phdsymp.tex
reformulate engine selection
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@156 43ef1190-90fd-4dd7-a769-d0121f02b80e

With the currently published benchmarks, it is up to the user to
select an engine with the best characteristics, relative to their own
expected application. However, I am often asked the question: ``what
is the best general-purpose triple store?'' Those who ask are usually not
prepared to expand on the question. Thus, we should ask ourselves: 
Can we collapse all the metrics into a single \emph{test
  statistic} that can summarize the performance of the engine as a
whole? Also, can we provide a system for developers that they can use
to see if any changes they do to the engine can have unexpected adverse
effects on other parts of the system? For those who are able to
qualify their inquiry, weighing different parts of the system or
metrics is more useful and will yield a more tenable answer, and
motivates the question: Can we use the system to better find the
distinguishing characteristics so that we can return a question that
will actually help new users of SPARQL engines to chose one that meets
their needs?

The above relies on data and queries that are representative of the
system as a whole. It is often asserted that it is not possible to
create a ``one-size-fits-all'' benchmark but answering the above
question requires such a benchmark.

>>>>

With the currently published benchmarks, it is up to the user to
select an engine with the best characteristics, relative to their own
expected application. New users often are unable to formulate
\emph{any} relevant expectations. For these users, the wide variety of
benchmarks, for instance by the TPC, offers little help as a thorough
understanding of the benchmarks and what they measure is required to
select an engine. To help these users, we should ask ourselves:
Can we collapse all the metrics into a single \emph{test
  statistic} that can summarize the performance of the engine as a
whole? Also, can we provide a system for developers that they can use
to see if any changes they do to the engine can have unexpected adverse
effects on other parts of the system? For those who can formulate
relevant expectations, weighing different parts of the system or
metrics is more useful and will yield a more tenable answer, and
motivates the question: Can we use the system to better find the
distinguishing characteristics so that we can return a question that
will actually help new users of SPARQL engines to chose one that meets
their needs?

The above relies on data and queries that are representative of the
system as a whole. It is often asserted that it is not possible to
create a ``one-size-fits-all'' benchmark but answering the above
question requires such a benchmark. The relative simplicity of RDF and
SPARQL may make this feasible.
